Characterizing Signal Loss, Error, and Bias in the 21cm Reionization \\Power Spectrum: A Revised Study of PAPER-64

### 2018-04-04 PAPER.tex
altered language about 3 variations: cosmic variance, noise, signal loss

One issue to address is how one incorporates the randomness of $\widehat{P}_{\rm out}$ into our signal loss corrections. A different realization of the mock EoR signal is injected with each bootstrap run, causing the output to vary in two ways ---  there is a variation driven by the random seed (i.e. cosmic variance) and a variation caused by whether the injected signal looks more or less ``like'' the data (i.e. how much coupling there is, which affects how much loss results). For each injection level, the true $P_{\rm in}$ is simply the average of our bootstrapped estimates $\widehat{P}_{\rm in}$.

Phrased in the context of Bayes' rule, we wish to find the posterior probability distribution $p(P_{\rm in} | 
\widehat{P}_{\rm out})$, which is the probability of $P_{\rm in}$ given the uncorrected/measured power spectrum estimate $\widehat{P}_{\rm out}$.  Bayes' rule relates the posterior, which we don't know, to the likelihood, which we can forward model. In other words,

@@

The implementation details of the injection process require some more detailed explanation. In our code, we add a new realization of EoR to each independent bootstrap of data (see Section \ref{sec:Boot} for a description of PAPER's bootstrapping routine) with the goal of simultaneously capturing variance due to noise and signal loss. To limit computing time we perform $20$ realizations of each $P_{\rm in}$ level. We also run $50$ total EoR injection levels, yielding $P_{\rm in}$ values that range from $\sim$$10^{5}$\,mK$^{2}$ ($h^{-1}$ Mpc)$^{3}$ to $\sim$10$^{11}$\,mK$^{2}$ ($h^{-1}$ Mpc)$^{3}$, resulting in a total of $1000$ data points on our $P_{\rm in}$ vs. $\widehat{P}_{\rm out}$ grid.

Going forward, we treat every $k$-value separately in order to determine an upper limit on the EoR signal per $k$. We bin our simulation outputs along the $P_{\rm in}$ axis, and smooth the distribution of $\widehat{P}_{\rm out}$ values using kernel density estimators (\citealt{scott2008kernel}) for each bin (and normalizing them). Stitching all of them together results in a 2-dimensional smoothed transfer function, shown in Figure \ref{fig:sigloss_transfercurve} for both the weighted (left) and unweighted (right) cases. Although we only show figures for one $k$-value, we note that 
the shape of the transfer curve is similar for all $k$'s. This transfer function is the likelihood function in Bayes' rule, namely $\mathcal{L} (  \widehat{P}_{\rm out} | P_{\rm in})$.  We then invoke Bayes' interpretation and re-interpret it as the posterior $p(P_{\rm in}|\widehat{P}_{\rm out})$ where we recall that $\widehat{P}_{\rm out}$ is a model of our data. To do this we make a horizontal cut across at the data value $\widehat{\textbf{P}}_{x}$ (setting $\widehat{P}_{\rm out} = \widehat{\textbf{P}}_{x}$) and assume a uniform prior to yield a posterior distribution for the signal. We compute the $95\%$ confidence interval (an upper limit on EoR) from these distributions.

>>>>

One issue to address is how one incorporates the randomness of $\widehat{P}_{\rm out}$ into our signal loss corrections. A different realization of the mock EoR signal is injected with each bootstrap run, causing the output to vary in three ways ---  there is noise variation from the bootstraps, there is cosmic variation from generating multiple realizations of the mock EoR signal, and there is a variation caused by whether the injected signal looks more or less ``like'' the data (i.e. how much coupling there is, which affects how much loss results).

For each injection level, the true $P_{\rm in}$ is simply the average of our bootstrapped estimates $\widehat{P}_{\rm in}$, since $\widehat{P}_{\rm in, \alpha}$ is by construction an unbiased estimator. Phrased in the context of Bayes' rule, we wish to find the posterior probability distribution $p(P_{\rm in} | 
\widehat{P}_{\rm out})$, which is the probability of $P_{\rm in}$ given the uncorrected/measured power spectrum estimate $\widehat{P}_{\rm out}$.  Bayes' rule relates the posterior, which we don't know, to the likelihood, which we can forward model. In other words,

@@

The implementation details of the injection process require some more detailed explanation. In our code, we add a new realization of EoR to each independent bootstrap of data (see Section \ref{sec:Boot} for a description of PAPER's bootstrapping routine) with the goal of simultaneously capturing cosmic variance, noise variance, and signal loss. To limit computing time we perform $20$ realizations of each $P_{\rm in}$ level. We also run $50$ total EoR injection levels, yielding $P_{\rm in}$ values that range from $\sim$$10^{5}$\,mK$^{2}$ ($h^{-1}$ Mpc)$^{3}$ to $\sim$10$^{11}$\,mK$^{2}$ ($h^{-1}$ Mpc)$^{3}$, resulting in a total of $1000$ data points on our $P_{\rm in}$ vs. $\widehat{P}_{\rm out}$ grid.

Going forward, we treat every $k$-value separately in order to determine an upper limit on the EoR signal per $k$. We bin our simulation outputs along the $P_{\rm in}$ axis (one bin per injection level), and smooth the distribution of $\widehat{P}_{\rm out}$ values using kernel density estimators (\citealt{scott2008kernel}) for each bin (and normalize them). Stitching all of them together results in a 2-dimensional smoothed transfer function, shown in Figure \ref{fig:sigloss_transfercurve} for both the weighted (left) and unweighted (right) cases. Although we only show figures for one $k$-value, we note that 
the shape of the transfer curve is similar for all $k$'s. This transfer function is the likelihood function in Bayes' rule, namely $\mathcal{L} (  \widehat{P}_{\rm out} | P_{\rm in})$.  We then invoke Bayes' interpretation and re-interpret it as the posterior $p(P_{\rm in}|\widehat{P}_{\rm out})$ where we recall that $\widehat{P}_{\rm out}$ is a model of our data. To do this we make a horizontal cut across at the data value $\widehat{\textbf{P}}_{x}$ (setting $\widehat{P}_{\rm out} = \widehat{\textbf{P}}_{x}$) and assume a uniform prior to yield a posterior distribution for the signal. We compute the $95\%$ confidence interval (an upper limit on EoR) from these distributions.
